---
title: "Pooled WBL Analyses"
author: "Will Schulz"
date: "2023-05-10"
output: html_document
---

```{r}
library(tidyverse)
library(jsonlite)
library(sandwich)
library(stargazer)
```


# Data Parsing & Cleaning

```{r}
# Load & Parse JSON to friendly-ish dataframe

lines <- c(read_lines("../../../data/batch_WBL_Pilot_1_01GW7XWRTED6ESDBC6YCZXMYK9.jsonl"),
           read_lines("../../../data/batch_WBL_Pilot_2_01GWMV07SHB8GEEMR6AV5ATGYR.jsonl"),
           read_lines("../../../data/batch_WBL_Pilot_3_01GZH6BMFYWDC8QBSX0Z841KXX.jsonl")
           )

json <- lines %>% lapply(., jsonlite::fromJSON)

str(json[[7]]$recordingIds)
str(json[[7]]$consent)
str(json[[8]]$recordingIds)

raw_data <- json %>% sapply(function(x) x[which(sapply(x, function(y) (length(y)==1 & !is.list(y))))]) %>% do.call(bind_rows, .)

raw_data$recordingIds <- json %>% sapply(function(x) x$recordingIds)

lists <- list()
for (i in c("consent", "config", "introSequence")){
  lists[[i]] <- json %>% sapply(function(x) x[[i]]) %>% apply(., 2, list) %>% unlist(., recursive = F)
}

for (i in c("treatment", "surveys", "prompts", "qualtrics", "QCSurvey", "exportErrors")){
  lists[[i]] <- json %>% sapply(function(x) x[[i]])
}

raw_data <- cbind(raw_data, do.call(cbind, lists))
#raw_data

rm(lists, json, i)
```


```{r}
#parse timeArrived
raw_data$timeArrived <- as.POSIXct(raw_data$timeArrived/1000, origin = "1970-01-01 UTC")
```


```{r}
# recordingIds_tosave <- raw_data$recordingIds
# 
# names(recordingIds_tosave) <- raw_data$deliberationId
# 
# recordingIds_tosave
# 
# jsonlite::write_json(recordingIds_tosave, path = "recordingIds_for_chris.json")
```


## Clean Survey/Prompts

```{r}
get_value <- function(x){
  return(x$value)
}

prompts <- sapply(raw_data$prompts, sapply, get_value)
prompt_names <- unique(names(unlist(prompts)))
```


```{r}
empty_vec <- rep(NA, length(prompt_names))
names(empty_vec) <- prompt_names

a <- sapply(prompts, function(x) unlist(x[prompt_names], recursive = F))
for (i in which(sapply(a, is.null))){a[[i]] <- empty_vec}
b <- (t(sapply(a, function(x) as.numeric(x[prompt_names]))))
colnames(b) <- prompt_names %>% str_replace(pattern = ".*/bad_influence/police_", "")

#b
```


```{r}
d <- cbind(raw_data, b)
```


## Process Survey Data

What are the levels of the variable "education"?

Did we measure ideology?

What does "independent importance" mean?  How was this question asked?


```{r include = F}
# do surveys next
#raw_data$surveys[[1]]
#str(raw_data$surveys[[1]])

raw_data$surveys[[13]]$survey_PoliticalPartyUS_intro_3$responses

raw_data$surveys[[1]]$survey_PoliticalPartyUS_intro_3

raw_data$surveys[[1]]$survey_PoliticalPartyUS_intro_3$responses$party
raw_data$surveys[[1]]$survey_PoliticalPartyUS_intro_3$responses$democratStrength
raw_data$surveys[[1]]$survey_PoliticalPartyUS_intro_3$responses$democratImportance

raw_data$surveys[[2]]$survey_PoliticalPartyUS_intro_3$responses$independentLean
raw_data$surveys[[2]]$survey_PoliticalPartyUS_intro_3$responses$independentImportance

raw_data$surveys[[19]]$survey_PoliticalPartyUS_intro_3$responses$republicanStrength
raw_data$surveys[[19]]$survey_PoliticalPartyUS_intro_3$responses$republicanImportance
```


```{r}
d$gender <- sapply(raw_data$surveys, function(x) x$survey_Demographics_exit_4$responses$gender) %>% as.character()
d$gender[which(d$gender == "NULL")] <- NA

d$education <- sapply(raw_data$surveys, function(x) x$survey_Demographics_exit_4$responses$education_US) %>% as.character()
d$education[which(d$education == "NULL")] <- NA

d$party <- sapply(raw_data$surveys, function(x) x$survey_PoliticalPartyUS_intro_3$responses$party) %>% as.character()
d$party[which(d$party == "NULL")] <- NA

d$democratStrength <- sapply(raw_data$surveys, function(x) x$survey_PoliticalPartyUS_intro_3$responses$democratStrength) %>% as.character()
d$democratStrength[which(d$democratStrength == "NULL")] <- NA

d$democratImportance <- sapply(raw_data$surveys, function(x) x$survey_PoliticalPartyUS_intro_3$responses$democratImportance) %>% as.character()
d$democratImportance[which(d$democratImportance == "NULL")] <- NA

d$republicanStrength <- sapply(raw_data$surveys, function(x) x$survey_PoliticalPartyUS_intro_3$responses$republicanStrength) %>% as.character()
d$republicanStrength[which(d$republicanStrength == "NULL")] <- NA

d$republicanImportance <- sapply(raw_data$surveys, function(x) x$survey_PoliticalPartyUS_intro_3$responses$republicanImportance) %>% as.character()
d$republicanImportance[which(d$republicanImportance == "NULL")] <- NA

d$independentLean <- sapply(raw_data$surveys, function(x) x$survey_PoliticalPartyUS_intro_3$responses$independentLean) %>% as.character()
d$independentLean[which(d$independentLean == "NULL")] <- NA

d$independentImportance <- sapply(raw_data$surveys, function(x) x$survey_PoliticalPartyUS_intro_3$responses$independentImportance) %>% as.character()
d$independentImportance[which(d$independentImportance == "NULL")] <- NA

#d
```


```{r}
# construct partisanship scale

d <- d %>% mutate(pid_7 = case_when(democratStrength == "Strong Democrat" ~ (-3),
                                    democratStrength == "Not very strong Democrat" ~ (-2),
                                    independentLean == "Closer to Democratic Party" ~ (-1),
                                    independentLean == "Neither" ~ (0),
                                    independentLean == "Closer to Republican Party" ~ (1),
                                    republicanStrength == "Not very strong Republican" ~ (2),
                                    republicanStrength == "Strong Republican" ~ (3),
                                    ),
                  pid_strength = abs(pid_7))

#d
```



```{r}
# constructive listening, other satisfaction...

```



# Cleaning and Processing

## Make Additive and PCA Indices of policing qs

```{r}
pre_pca <- psych::principal(d %>% select(ends_with("stage_0")), nfactors = 1, rotate = "varimax", missing=TRUE, impute = "mean")#$scores[,1]
# pre_pca
# str(pre_pca$loadings)
# pre_pca$scores
```


```{r}
policing_loading_signs <- sign(pre_pca$loadings[1:7])
#policing_loading_signs
```


```{r}
#make additive scale
d$police_additive_pre <- d %>% select(ends_with("stage_0")) %>% as.matrix %>% {. %*% policing_loading_signs}
d$police_additive_post <- d %>% select(ends_with("stage_3")) %>% as.matrix %>% {. %*% policing_loading_signs}


#impute missing with pca
d$police_pca_pre <- pre_pca$scores %>% as.numeric
d$police_pca_post <- psych::predict.psych(pre_pca, data = d %>% select(ends_with("stage_3")), impute = "means") %>% as.numeric

#drop PCA to NA wherever respondent answered less than half of relevant questions
d$police_pca_pre[d %>% select(ends_with("stage_0")) %>% as.matrix %>% is.na %>% rowMeans() %>% {.>.7}] <- NA
d$police_pca_post[d %>% select(ends_with("stage_3")) %>% as.matrix %>% is.na %>% rowMeans() %>% {.>.7}] <- NA
```


## Define Treatment Variable

```{r}
for (i in 1:nrow(d)){
  #print(i)
  #try(d$group_treatment[i] <- if_else(d$treatment[[i]]$name=="assigned_leader", true = 1, false = 0), silent = T)
  if (!is.null(d$treatment[[i]]$name)){
    d$group_treatment[i] <- if_else(d$treatment[[i]]$name=="assigned_leader", true = 1, false = 0)
  } else {d$group_treatment[i] <- NA}
}
```


# Analyses


## Group Polarization

```{r}
mean(abs(d$police_pca_pre), na.rm = T)
mean(abs(d$police_pca_post), na.rm = T)

d$police_pca_pre %>% hist
d$police_pca_post %>% hist

d$police_pca_pre %>% var(., na.rm = T)
d$police_pca_post %>% var(., na.rm = T)

var.test(d$police_pca_post, d$police_pca_pre) #not significant
```



## Leader Influence in Treated Groups

```{r}
d_t <- d %>% filter(group_treatment==1)
#d_t
```


```{r}
#d_t_nonleader$alter_nonleader_police_additive_pre <- 

for (i in 1:nrow(d_t)){
  d_t$alter_leader_police_additive_pre[i] <- NA
  d_t$alter_nonleader_police_additive_pre[i] <- NA
  d_t$alter_leader_police_pca_pre[i] <- NA
  d_t$alter_nonleader_police_pca_pre[i] <- NA
  if (d_t$position[i] != 0){
    d_t$alter_nonleader_police_additive_pre[i] <- d_t %>% filter((gameId == d_t$gameId[i]) & (deliberationId != d_t$deliberationId[i])) %>% filter(position != 0) %>% pull(police_additive_pre)
    d_t$alter_leader_police_additive_pre[i] <- d_t %>% filter((gameId == d_t$gameId[i]) & (deliberationId != d_t$deliberationId[i])) %>% filter(position == 0) %>% pull(police_additive_pre)
    d_t$alter_nonleader_police_pca_pre[i] <- d_t %>% filter((gameId == d_t$gameId[i]) & (deliberationId != d_t$deliberationId[i])) %>% filter(position != 0) %>% pull(police_pca_pre)
    d_t$alter_leader_police_pca_pre[i] <- d_t %>% filter((gameId == d_t$gameId[i]) & (deliberationId != d_t$deliberationId[i])) %>% filter(position == 0) %>% pull(police_pca_pre)
  }
}

# what's the difference between gameId and recordingRoomName? which should I use in this code?
# is deliberationId an appropriate person-identifier?  Is it constant across disconnect/reconnects?  When/how is it assigned?

#d_t
```


```{r}
# d_t$position
# 
# d_t$alter_leader_police_additive_pre[which(d_t$position != 0)]
# d_t$alter_nonleader_police_additive_pre[which(d_t$position != 0)]
# 
# d_t$alter_leader_police_pca_pre[which(d_t$position != 0)]
# d_t$alter_nonleader_police_pca_pre[which(d_t$position != 0)]
```


```{r}
d_t_nonleader <- d_t %>% filter(position!=0)
#d_t_nonleader

# d_t_nonleader$alter_leader_police_pca_pre[which(d_t_nonleader$position != 0)]
# d_t_nonleader$alter_nonleader_police_pca_pre[which(d_t_nonleader$position != 0)]
```


### Leader Influence Models

treatment effect: in groups that had an assigned leader, was the leader significantly more persuasive (than the non-leaders) to the non-leaders?

```{r}
lm_leaderinfluence_1 <- lm(police_pca_post ~ police_pca_pre + alter_nonleader_police_pca_pre + alter_leader_police_pca_pre, data = d_t_nonleader)
#lm_leaderinfluence_1 %>% summary 

lm_leaderinfluence_2 <- lm(police_pca_post ~ alter_nonleader_police_pca_pre + alter_leader_police_pca_pre, data = d_t_nonleader)
#lm_leaderinfluence_2 %>% summary 
```


```{r}
make_robust_se <- function(mod){
  cov1         <- sandwich::vcovCL(mod, cluster = ~gameId)
  robust_se    <- sqrt(diag(cov1))
  return(robust_se)
}
```


```{r, results='asis'}
stargazer::stargazer(lm_leaderinfluence_1,
                     lm_leaderinfluence_2,
                     type = "text",
                     se = list(make_robust_se(lm_leaderinfluence_1),make_robust_se(lm_leaderinfluence_2)))

```


## Descriptive Analysis of Influence

Model influence as a latent force-multiplier?


```{r}
library(rstan)
options(mc.cores = 2)
```


### Leader treatment only

```{r}
# Clean data for leader-treatment-only model
d_clean <- d %>% filter(!is.na(gameId))
bad_game_ids <- d_clean %>% filter(is.na(police_pca_pre) | is.na(police_pca_post)) %>% pull(gameId)
d_clean <- d_clean %>% filter(!gameId %in% bad_game_ids)
d_clean <- d_clean %>% filter(gameId != "01GWMVKGSJ61RGH3KRTQ21EH01")
#d_clean

d_clean$gender[which(is.na(d_clean$gender))] <- rep("not_provided", sum(is.na(d_clean$gender))) #assume everyone who didn't provide a gender is not male (this is wrong and bad, fix this later)

alter_1 <- rep(NA, nrow(d_clean))
alter_2 <- rep(NA, nrow(d_clean))
for (i in 1:nrow(d_clean)){
  alters_deliberationIds <- d_clean %>% filter(gameId == d_clean$gameId[i] & deliberationId != d_clean$deliberationId[i]) %>% pull(deliberationId)
  try(alter_1[i] <- which(d_clean$deliberationId == alters_deliberationIds[1]), silent = T)
  try(alter_2[i] <- which(d_clean$deliberationId == alters_deliberationIds[2]), silent = T)
}

stan_dat <- list(N = nrow(d_clean),
                 pre = d_clean$police_pca_pre,
                 post = d_clean$police_pca_post,
                 alter_1 = alter_1,
                 alter_2 = alter_2,
                 is_leader = d_clean$group_treatment==1 & d_clean$position==0,
                 has_leader = d_clean$group_treatment==1
                 )
#stan_dat
```


```{stan, output.var="leader_treatment"}
data {
  int<lower=1> N;                  //number of data points
  real pre[N];     //outcome: post-discussion attitude scale
  real post[N];     //outcome: post-discussion attitude scale
  int<lower=1> alter_1[N];     //alter 1 id (maybe N-1?)
  int<lower=1> alter_2[N];     //alter 2 id (maybe N-1?)
  int<lower=0,upper=1> is_leader[N];     //leader indicator
  int<lower=0,upper=1> has_leader[N];     //leader indicator
}

parameters {
  real post_intercept;           // intercept of post-discussion attitude model
  real aw_intercept;             // alter weight intercept
  real aw_leader;             // alter weight leader (0 if group untreated)
  real self_weight;             // self weight
  real has_leader_intercept;
  real<lower=0> sigma;//disturbance to outcome model (need to cluster this)
}

model {
  real alter_1_weight;
  real alter_2_weight;
  
  for (i in 1:N){
    alter_1_weight = aw_intercept + aw_leader * is_leader[alter_1[i]];
    alter_2_weight = aw_intercept + aw_leader * is_leader[alter_2[i]];
    post[i] ~ normal(post_intercept + has_leader[i] * has_leader_intercept + pre[i] * self_weight + pre[alter_1[i]] * alter_1_weight + pre[alter_2[i]] * alter_2_weight, sigma);
  }
}

```


```{r}
#estimate
test_fit <- sampling(leader_treatment,
                 data = stan_dat,
                 chains = 2, iter = 1000)

pairs(test_fit, pars = c("aw_intercept", "aw_leader", "post_intercept", "self_weight"))
plot(test_fit)
```



```{r}
d_clean <- d %>% filter(!is.na(gameId))# %>% filter(!is.na(police_pca_pre)) %>% filter(!is.na(police_pca_post))

bad_game_ids <- d_clean %>% filter(is.na(police_pca_pre) | is.na(police_pca_post) | is.na(pid_strength)) %>% pull(gameId)

d_clean <- d_clean %>% filter(!gameId %in% bad_game_ids)

d_clean <- d_clean %>% filter(gameId != "01GWMVKGSJ61RGH3KRTQ21EH01")
#d_clean

#d_clean$pid_strength[which(is.na(d_clean$pid_strength))] <- 3 #hack: treat the DSA person as a "very strong partisan"
#d_clean$pid_strength[which(is.na(d_clean$pid_strength))] <- 0

d_clean$gender[which(is.na(d_clean$gender))] <- rep("not_provided", sum(is.na(d_clean$gender))) #assume everyone who didn't provide a gender is not male (this is wrong and bad, fix this later)
```


```{r}
alter_1 <- rep(NA, nrow(d_clean))
alter_2 <- rep(NA, nrow(d_clean))
for (i in 1:nrow(d_clean)){
  alters_deliberationIds <- d_clean %>% filter(gameId == d_clean$gameId[i] & deliberationId != d_clean$deliberationId[i]) %>% pull(deliberationId)
  try(alter_1[i] <- which(d_clean$deliberationId == alters_deliberationIds[1]), silent = T)
  try(alter_2[i] <- which(d_clean$deliberationId == alters_deliberationIds[2]), silent = T)
}

stan_dat <- list(N = nrow(d_clean),
                 pre = d_clean$police_pca_pre,
                 post = d_clean$police_pca_post,
                 alter_1 = alter_1,
                 alter_2 = alter_2,
                 is_leader = d_clean$group_treatment==1 & d_clean$position==0,
                 has_leader = d_clean$group_treatment==1,
                 male = d_clean$gender=="male",
                 pid_strength = d_clean$pid_strength
                 )

stan_dat
```


```{stan, output.var="demographics"}
// still need to cluster SEs in this
data {
  int<lower=1> N;                  //number of data points
  real pre[N];     //outcome: post-discussion attitude scale
  real post[N];     //outcome: post-discussion attitude scale
  int<lower=1> alter_1[N];     //alter 1 id (maybe N-1?)
  int<lower=1> alter_2[N];     //alter 2 id (maybe N-1?)
  int<lower=0,upper=1> male[N];     //male gender indicator
  int<lower=0> pid_strength[N];     //
}

parameters {
  real post_intercept;           // intercept of post-discussion attitude model
  real aw_intercept;             // alter weight intercept
  real aw_male;             // alter weight male gender
  real aw_pid_strength;             // alter weight male gender
  real self_weight;             // self weight
  real<lower=0> sigma;//disturbance to outcome model (for clustering, allow sigma to vary across groups?)
}

model {
  real alter_1_weight;
  real alter_2_weight;
  
  for (i in 1:N){
    alter_1_weight = aw_intercept + aw_male * male[alter_1[i]] + aw_pid_strength * pid_strength[alter_1[i]];
    alter_2_weight = aw_intercept + aw_male * male[alter_2[i]] + aw_pid_strength * pid_strength[alter_2[i]];
    post[i] ~ normal(post_intercept + pre[i] * self_weight + pre[alter_1[i]] * alter_1_weight + pre[alter_2[i]] * alter_2_weight, sigma);
  }
}

```


```{r}
test_fit <- sampling(demographics,
                 data = stan_dat,
                 chains = 2, iter = 1000)
#saveRDS(test_fit, "bi_obs_influence_fit_1k.rds")

pairs(test_fit, pars = c("aw_intercept", "aw_male", "post_intercept", "self_weight"))
plot(test_fit)
```



# With Leader Treatment

Version that includes the leader treatment, in addition to gender and pid strength

```{stan, output.var="treatment_and_demos"}
// this may be an appropriate way to model leader effects using the pooled sample, but I think we don't have enough observations to estimate this rn
// still need to cluster SEs in this
data {
  int<lower=1> N;                  //number of data points
  real pre[N];     //outcome: post-discussion attitude scale
  real post[N];     //outcome: post-discussion attitude scale
  int<lower=1> alter_1[N];     //alter 1 id (maybe N-1?)
  int<lower=1> alter_2[N];     //alter 2 id (maybe N-1?)
  int<lower=0,upper=1> male[N];     //male gender indicator
  int<lower=0> pid_strength[N];     //
  int<lower=0,upper=1> is_leader[N];     //leader indicator
  int<lower=0,upper=1> has_leader[N];     //leader indicator
}

parameters {
  real post_intercept;           // intercept of post-discussion attitude model
  real aw_intercept;             // alter weight intercept
  real aw_male;             // alter weight male gender
  real aw_pid_strength;             // alter weight male gender
  real aw_leader;             // alter weight leader (0 if group untreated)
  real self_weight;             // self weight
  real has_leader_intercept;
  real<lower=0> sigma;//disturbance to outcome model (need to cluster this)
}

model {
  real alter_1_weight;
  real alter_2_weight;
  
  for (i in 1:N){
    alter_1_weight = aw_intercept + aw_male * male[alter_1[i]] + aw_pid_strength * pid_strength[alter_1[i]] + aw_leader * is_leader[alter_1[i]];
    alter_2_weight = aw_intercept + aw_male * male[alter_2[i]] + aw_pid_strength * pid_strength[alter_2[i]] + aw_leader * is_leader[alter_2[i]];
    post[i] ~ normal(post_intercept + has_leader[i] * has_leader_intercept + pre[i] * self_weight + pre[alter_1[i]] * alter_1_weight + pre[alter_2[i]] * alter_2_weight, sigma);
  }
}

```


```{r}
test_fit <- sampling(treatment_and_demos,
                 data = stan_dat,
                 #init = init_1,
                 chains = 2, iter = 1000)
#saveRDS(test_fit, "bi_obs_exp_influence_fit_1k.rds")

pairs(test_fit, pars = c("aw_intercept", "aw_male", "has_leader_intercept", "aw_leader", "post_intercept", "self_weight"))
#pairs(test_fit, pars = c("aw_intercept", "has_leader_intercept", "aw_leader", "post_intercept"))
```


```{r}
pairs(test_fit, pars = c("has_leader_intercept", "aw_leader"))
```


```{r}
plot(test_fit)
```



# Indicator Version of fully-saturated

Replace alters' pre-opinions with signed indicators for alter's pre positions relative to the ego

```{stan, output.var="treatment_and_demos_indicator"}
// this may be an appropriate way to model leader effects using the pooled sample, but I think we don't have enough observations to estimate this rn
// still need to cluster SEs in this

functions {
  // ... function declarations and definitions ...
  int signnum(real x) {
    return x < 0 ? -1 : x > 0;
  }
}

data {
  int<lower=1> N;                  //number of data points
  real pre[N];     //outcome: post-discussion attitude scale
  real post[N];     //outcome: post-discussion attitude scale
  int<lower=1> alter_1[N];     //alter 1 id (maybe N-1?)
  int<lower=1> alter_2[N];     //alter 2 id (maybe N-1?)
  int<lower=0,upper=1> male[N];     //male gender indicator
  int<lower=0> pid_strength[N];     //
  int<lower=0,upper=1> is_leader[N];     //leader indicator
  int<lower=0,upper=1> has_leader[N];     //leader indicator
}

parameters {
  real post_intercept;           // intercept of post-discussion attitude model
  real aw_intercept;             // alter weight intercept
  real aw_male;             // alter weight male gender
  real aw_pid_strength;             // alter weight male gender
  real aw_leader;             // alter weight leader (0 if group untreated)
  real self_weight;             // self weight
  real has_leader_intercept;
  real<lower=0> sigma;//disturbance to outcome model (need to cluster this)
}

model {
  real alter_1_weight;
  real alter_2_weight;
  
  for (i in 1:N){
    alter_1_weight = aw_intercept + aw_male * male[alter_1[i]] + aw_pid_strength * pid_strength[alter_1[i]] + aw_leader * is_leader[alter_1[i]];
    alter_2_weight = aw_intercept + aw_male * male[alter_2[i]] + aw_pid_strength * pid_strength[alter_2[i]] + aw_leader * is_leader[alter_2[i]];
    post[i] ~ normal(post_intercept + has_leader[i] * has_leader_intercept + pre[i] * self_weight + signnum(pre[alter_1[i]] - pre[i]) * alter_1_weight + signnum(pre[alter_2[i]] - pre[i]) * alter_2_weight, sigma);
  }
}

```


```{r}
test_fit <- sampling(treatment_and_demos_indicator,
                 data = stan_dat,
                 #init = init_1,
                 chains = 2, iter = 1000)
#saveRDS(test_fit, "bi_obs_exp_influence_indicator_fit_1k.rds")

pairs(test_fit, pars = c("aw_intercept", "aw_male", "has_leader_intercept", "aw_leader", "post_intercept", "self_weight"))
#pairs(test_fit, pars = c("aw_intercept", "has_leader_intercept", "aw_leader", "post_intercept"))
```


```{r}
pairs(test_fit, pars = c("has_leader_intercept", "aw_leader"))
```


```{r}
plot(test_fit)
```



```{r}


```


```{r}


```


